Communicating causal effect heterogeneity

### 2024-08-26 index.qmd
Fix figure

p2_pars_target <- post2 |> 
  select(contains("target")) |> 
  rename_with(
    ~str_to_lower(.) |> 
      str_remove("target_") |> 
      str_remove_all("_task")
  ) |> 
  pivot_longer(everything()) |> 
  separate(name, c("type", "group"), extra = "merge") |> 
  mutate(
    type = factor(
      type, 
      levels = c("sd", "pd", "ratio", "cor"),
      labels = c("SD", "p+", "Heterogeneity ratio", "Cor(Free, Cued)")
    ),
    group = factor(
      group,
      levels = c("free", "cued", "difference", "free_cued"),
      labels = c("Free", "Cued", "Difference", "Correlation")
    ) |> fct_rev(),
    value = if_else(type == "Heterogeneity ratio" & abs(value) > 5, NaN, value)
  ) |> 
  ggplot(aes(value, group, color = group, fill = group)) +
  scale_color_manual(
    "Recall task",
    values = c(rep("#7570B3", 2), "#D95F02", "#1B9E77"),
    aesthetics = c("color", "fill")
  ) +
  scale_y_discrete(
    expand = expansion(c(0.1, 0.25))
  ) +
  scale_x_continuous(
    "Parameter value",
    expand = expansion(0.1)
  ) +
  stat_histinterval(
    breaks = 50,
    normalize = "panels",
    .width = .95,
    size = 1,
    slab_alpha = 0.35,
    justification = 0.01
  ) +
  facet_wrap("type", ncol = 1, scales = "free") +
  theme(
    legend.position = "none",
    panel.spacing = unit(0, "pt"),
    axis.title.y = element_blank()
  )

p2_cdf_target <- tmp_target |> 
  ggplot(aes(x = x)) +
  aes(y = cdf, ymin = cdf.lower, ymax = cdf.upper, col = Task, fill = Task) +
  scale_color_brewer(
    "Recall task",
    palette = "Dark2",
    aesthetics = c("color", "fill"),
    direction = -1
  ) +
  scale_x_continuous(
    TeX("$\\Phi(Pr(Correct))$"),
    expand = expansion(0.01),
    breaks = extended_breaks(5),
    sec.axis = sec_axis(
      name = "Proportion correct",
      trans = ~pnorm(.), 
      breaks = c(0.05, .1, .3, .5, .7, .9, .95),
      labels = c(".05", ".1", ".3", ".5", ".7", ".9", ".95")
    )
  ) +
  scale_y_continuous(
    breaks = extended_breaks(7),
    expand = expansion(c(0.005, 0.005))
  ) +
  ylab("CDF") +
  geom_ribbon(
    alpha = .2, col = NA
  ) +
  geom_line(
    linewidth = .5
  ) +
  theme(
    legend.position = "none",
    panel.spacing = unit(0, "pt"),
    panel.border = element_rect(fill = NA)
  )

>>>>

p2_pars_target <- post2 |> 
  select(contains("target"), -sd_target_ratio) |> 
  rename_with(
    ~str_to_lower(.) |> 
      str_remove("target_") |> 
      str_remove_all("_task")
  ) |> 
  pivot_longer(everything()) |> 
  separate(name, c("type", "group"), extra = "merge") |> 
  mutate(
    type = factor(
      type, 
      levels = c("sd", "pd", "ratio", "cor"),
      labels = c("SD", "p+", "Heterogeneity ratio", "Cor(Free, Cued)")
    ),
    group = factor(
      group,
      levels = c("free", "cued", "difference", "free_cued"),
      labels = c("Free", "Cued", "Difference", "Correlation")
    ) |> fct_rev(),
    value = if_else(
      type == "Heterogeneity ratio" & abs(value) > 5, 
      NaN, 
      value
    )
  ) |> 
  ggplot(aes(value, group, color = group, fill = group)) +
  scale_color_manual(
    "Recall task",
    values = c(rep("#7570B3", 2), "#D95F02", "#1B9E77"),
    aesthetics = c("color", "fill")
  ) +
  scale_y_discrete(
    expand = expansion(c(0.1, 0.25))
  ) +
  scale_x_continuous(
    "Parameter value",
    expand = expansion(0.1)
  ) +
  stat_histinterval(
    breaks = 50,
    normalize = "panels",
    .width = .95,
    size = 1,
    slab_alpha = 0.35,
    justification = 0.01
  ) +
  facet_wrap("type", ncol = 1, scales = "free") +
  theme(
    legend.position = "none",
    panel.spacing = unit(0, "pt"),
    axis.title.y = element_blank()
  )

p2_cdf_target <- tmp_target |> 
  ggplot(aes(x = x)) +
  aes(
    y = cdf, ymin = cdf.lower, ymax = cdf.upper, 
    col = Task, fill = Task
  ) +
  scale_color_brewer(
    "Recall task",
    palette = "Dark2",
    aesthetics = c("color", "fill"),
    direction = -1
  ) +
  scale_x_continuous(
    TeX("$\\Phi(Pr(Correct))$"),
    expand = expansion(0.01),
    breaks = extended_breaks(5),
    sec.axis = sec_axis(
      name = "Proportion correct",
      trans = ~pnorm(.), 
      breaks = c(0.05, .1, .3, .5, .7, .9, .95),
      labels = c(".05", ".1", ".3", ".5", ".7", ".9", ".95")
    )
  ) +
  scale_y_continuous(
    breaks = extended_breaks(7),
    expand = expansion(c(0.005, 0.005))
  ) +
  ylab("CDF") +
  geom_ribbon(
    alpha = .2, col = NA
  ) +
  geom_line(
    linewidth = .5
  ) +
  theme(
    legend.position = "none",
    panel.spacing = unit(0, "pt"),
    panel.border = element_rect(fill = NA)
  )
